%\addcontentsline{toc}{section}{\textit{Executive Summary}}
\addcontentsline{toc}{section}{Executive Summary}

{The company owner has conveyed his scepticism about the growth potential and the company's current financial position, as the magnitude of new infrastructure projects to be launched in the local market was unlikely to be high due to the Covid-19 pandemic. He was also concerned about the lack of enough revenue generated. This led him to consider laying off certain employees and redesigning its organizational structure to control expenditure, to combat the issue of high operating costs & low revenue. This leads to the question: "Should the company, DDE, consider outsourcing their labour demands ?".}

\vspace{0.25cm}

{Primary data was gathered from an interview with the owner and questionnaires sent to the employees, managers, and previous customers. This data was analyzed using Lewin's force field analysis, SWOT analysis and fishbone diagram. Secondary data was gathered from the Balance sheet, Profit-Loss account and Cash-Flow statements to produce a ratio analysis to gauge the company's financial position.}

\vspace{0.25cm}

{This report suggests that the company's financial \& organizational structure is in a good position and is favourable for the plans that DDE wishes to employ (outsourcing labour). This would drastically increase its Net Profit Margin and reduce the operating costs. However, it's recommended to conduct further market research to test the report's validity on the recommendations provided.}

\vspace{0.5cm}

\raggedright

{\textbf{Word Count: 200}}

