{This investigation combined and utilised two primary and three secondary sources of data. An interview was conducted with the founder of DDE, Mr. Farid Ahamad, seeking his views and goals off of his business; this provided a detailed outline of the goals and objectives of the corporation and their current standing and performance in the market. A questionnaire consisting of 10 questions was created and was conducted during four business days of the company, DDE. The questionnaire was aimed at the employees, managers and previous customers of the company. The questionnaire was an MCQ (Multiple choice) type.}

{The questionnaire aimed to gauge the employees, managers, and some other previous customer's opinions on the quality of the construction work the company has delivered to the project consultants, contractors and how they think about the company's organisational structure and work environment. These data sources shall be used to understand where and how the company can better use more efficient methods of Finance & Accounting, Marketing, Human resource management and Operations management.}

{The IB Business Management textbook by Oxford University press was utilised as a secondary source to reference concepts mentioned and definitions.}

{Various business tools were employed to gather information to aid in the decision-making process. A SWOT analysis was employed as it analyses both the external and internal strengths and weaknesses and also analyses external threats and opportunities. Lewin's force field analysis was also used in to weigh the driving and the restraining forces for the start of the new initiative; Lastly, Ratio analysis was used to calculate the current and future financial position of the company if the company is to proceed with the initiative, which is to outsource its labour demands.}

