

\textbf{1) What type of business is DDE? How big is the business? What sort of business structure is employed ?}

{DDE is a small company with mainly one shareholder (plus an investor/sleeping partner with 20\% share). The company provides material, equipment, labour, and various general miscellaneous technical works related to the construction of general structures and buildings. The company has one office in Al Nahda area of Dubai, where the company's two white-collar employees manage the day-to-day business affairs.}

{DDE can be largely classified as a construction company. The company makes about an average of USD 50k (\$50,000) per project in revenue; DDE undertakes about three projects per month on an average. Resulting in about USD 150k in monthly revenue. The business employs a very simple business structure. I, the owner, instruct my three main employees at my office. They pass those instructions to other blue-collar employees and supervise them. This business is a profit entity.}

\textbf{2) How exactly has the business progressed and developed from the time you have started this business venture? How has your business growth been over the years ?}

{The growth in the business has been mainly for two reasons, recognition in the market amongst various contractors and consultants and marketing through multiple means of advertisements. The business has been steadily growing at a rate of approximately 20\% annually. Due to current market conditions due to the Covid-19 pandemic, the growth rate has decreased but has not stopped. To counter this, we have increased the budgets on the HR and marketing segments of the business. After some initial years after setting up the business, the company has shown a steady, consistent improvement from the time I have started this venture.}

\textbf{3) Why do you think this move to outsource labour would be beneficial for your company ?}

{I think this decision to outsource labour would be beneficial for the further growth of DDE as it would significantly reduce DDE's operating costs, increase the revenue generated and would lead DDE to undertake multiple projects than it can currently undertake as we would not need to depend on the company's labour. Therefore, it enables DDE to undertake as many projects as possible without the constraints of how to supply that much labour.}


